R Notebook

### 2020-01-29 src/comb-maxent.Rmd
progress on plots

```{r}
# outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
# wgsraster <- raster("../output/maxent/predictions/com-split/apr/cloglog_1998_04_0.50576.asc") #just chosen randomly to act as dummy file
# crs(wgsraster) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "
# outsidemcp <- spTransform(outsidemcp, crs(wgsraster))

@@

```{r bin probabilities}
#outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_1_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_1_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_2_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_2_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_3_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_3_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_4_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_4_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    #cumasc <- mask(cumasc, outsidemcp, inverse = TRUE)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_5_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_5_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

GO FROM HERE

>>>>

```{r}

@@

```{r bin probabilities}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_1_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_1_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_2_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_2_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_3_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_3_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_4_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_4_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_5_avgprob_", ascname, ".asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/prob_by_depth/", mth, "_binned_5_avgprob_", ascname, ".png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }

@@

histogram of probability by depth - by proportion

based on Remi's code
```{r}
require(data.table)
require(purrr)
require(lubridate)
require(tidyverse)

filenames <- list.files("../output/maxent/paper_plots/prob_by_depth/", pattern = "dis_prob_cells.csv", recursive = TRUE,full.names = TRUE)

all <- map_dfr(filenames, function(x) fread(x) %>% 
                       mutate(Month=substr(basename(x),1,3))) %>% 
  mutate(Probability = gsub(">0.9", "0.9 - 1", Probability),
         Depth = factor(round(Depth,1)),
         Depth = factor(Depth,ordered = TRUE, levels = rev(levels(Depth))),
         Month=factor(months(parse_date_time(Month,"%m")),
                      ordered = TRUE,
                      levels=months(parse_date_time(1:12,"%m"))))

#create a list of depths so you can set breaks for the x-axis (which is showing as the y-axis...)
dlst <- unique(all$Depth)
dlst <- as.character(dlst)
dlst <- as.numeric(dlst)
dlst <- sort(dlst)

#make the plot
  ggplot(all) +
  geom_col(aes(Depth, p_cells, fill = Probability),width=1) +
  coord_flip()+
  facet_wrap(~Month,ncol=5)+
  labs(y = "% Ocean at Depth", x = "Depth (meters)")+
  scale_fill_viridis(option="magma", discrete = TRUE, direction = -1, guide=guide_legend(nrow=2, byrow = TRUE))+
  theme_classic()+
  theme(legend.position = "bottom", axis.text.y = element_text(size=7), strip.background = element_blank()) +
  scale_x_discrete(breaks = c(dlst[1], dlst[5], dlst[10], dlst[15], dlst[20], dlst[25], dlst[30], dlst[35], dlst[40], dlst[47]))

ggsave("../output/maxent/paper_plots/test.png", dpi = 600)
```

# variable maps
- temp
- chl 
- o2
- sal
- 4 different months
- relationship of variables to each other
- pick a depth (say the 11.7737 m)

months are mar, jun, sep, dec
pick 3 diff years say 1998, 2006, 2013

```{r individual maps}
#aea <- raster("../output/env/aea.tif") #the correct CRS
s <- shapefile("../data/env/landp/land-wgs84v2.shp") #made in arcgis
crs(s) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
#acrs <- aea@crs
mcp <- shapefile("../output/bio/minimum_convex_poly/mcp-wgs84.shp")
#ss <- raster::intersect(s, mcp)  #trim land file to mcp

plotlist <- list()

yrlst <- c("1998", "2006", "2013")
mthlst <- c("03", "06", "09", "12")
varlst <- c("temp", "salinity", "o2")

pn <- 1
for (y in 1:length(yrlst)){
  yr <- yrlst[y]
  fdr <- paste0("../data/env/ascii-original/ascii", yr, "/")
  for (m in 1:length(mthlst)){
    mt <- mthlst[m]
    for (v in 1:length(varlst)){
      var <- varlst[v]
      ras <- raster(paste0(fdr, yr, "_", mt, "_", var, ".nc_11.7737.asc"))
      lyrnm <- names(ras)
      crs(ras) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
      #ras <- projectRaster(ras, aea)
      ras <- raster::mask(ras, mcp)

      plotlist[[pn]] <- levelplot(ras, margin=FALSE, colorkey=list(space='bottom', axis.line=list(col='black')), par.settings=list(axis.line=list(col='transparent')), scales=list(draw=FALSE), col.regions=colorRampPalette(blue2red(20))) + latticeExtra::layer(sp.polygons(s, fill = "dark grey", col = "transparent") ) #changed ss to s
      pn <- pn+1

     # png(paste0("../output/maxent/paper_plots/", lyrnm, ".png"), height = 1024, width = 1024)
     # print(p)
     # dev.off()
    }
  }
}

#chl is done seperately as it is surface

yrlst <- c("1998", "2006", "2013")
mthlst <- c("03", "06", "09", "12")
varlst <- c("chl")

for (y in 1:length(yrlst)){
  yr <- yrlst[y]
  fdr <- paste0("../data/env/ascii-original/ascii", yr, "/")
  for (m in 1:length(mthlst)){
    mt <- mthlst[m]
    for (v in 1:length(varlst)){
      var <- varlst[v]
      ras <- raster(paste0(fdr, yr, "_", mt, "_", var, ".nc_0.50576.asc"))
      lyrnm <- names(ras)
      crs(ras) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
      ras <- raster::mask(ras, mcp)
      plotlist[[pn]] <- levelplot(ras, margin=FALSE, colorkey=list(space='bottom', axis.line=list(col='black')), par.settings=list(axis.line=list(col='transparent')), scales=list(draw=FALSE), col.regions=colorRampPalette(blue2red(20))) + latticeExtra::layer(sp.polygons(s, fill = "dark grey", col = "transparent"))
      pn <- pn+1

   #   png(paste0("../output/maxent/paper_plots/", lyrnm, ".png"), height = 1024, width = 1024)
    #  print(p)
    #  dev.off()
    }
  }
}
```

### 2020-01-29 src/plots for paper.Rmd
progress on plots

binaryprob_list <- list.files("../output/maxent/paper_plots/hotspot_mapping/", pattern = ".*_bin_0.5_2d.asc", full.names = TRUE)
sum2d <- setNames(data.frame(matrix(ncol = 2, nrow = binl)), c("month", "count"))

>>>>

binaryprob_list <- list.files("../output/maxent/paper_plots/hotspot_mapping/", pattern = ".*_bin_0.5_2d.asc", full.names = TRUE)
sum2d <- setNames(data.frame(matrix(ncol = 2, nrow = binaryprob_list))), c("month", "count"))

### 2020-01-29 src/testing_file.Rmd
progress on plots

@@

mar11 <- raster("../output/maxent/predictions/mar/avg_cloglog_11.7737.asc")
mar61 <- raster("../output/maxent/predictions/mar/avg_cloglog_61.1128.asc")
mar199 <- raster("../output/maxent/predictions/mar/avg_cloglog_199.79.asc")
mar628 <- raster("../output/maxent/predictions/mar/avg_cloglog_628.026.asc")
mar11@crs <- acrs
mar61@crs <- acrs
mar199@crs <- acrs
mar628@crs <- acrs
mar11 <- raster::mask(mar11, mcp)
mar61 <- raster::mask(mar61, mcp)
mar199 <- raster::mask(mar199, mcp)
mar628 <- raster::mask(mar628, mcp)

jun11 <- raster("../output/maxent/predictions/jun/avg_cloglog_11.7737.asc")
jun61 <- raster("../output/maxent/predictions/jun/avg_cloglog_61.1128.asc")
jun199 <- raster("../output/maxent/predictions/jun/avg_cloglog_199.79.asc")
jun628 <- raster("../output/maxent/predictions/jun/avg_cloglog_628.026.asc")
jun11@crs <- acrs
jun61@crs <- acrs
jun199@crs <- acrs
jun628@crs <- acrs
jun11 <- raster::mask(jun11, mcp)
jun61 <- raster::mask(jun61, mcp)
jun199 <- raster::mask(jun199, mcp)
jun628 <- raster::mask(jun628, mcp)

sep11 <- raster("../output/maxent/predictions/sep/avg_cloglog_11.7737.asc")
sep61 <- raster("../output/maxent/predictions/sep/avg_cloglog_61.1128.asc")
sep199 <- raster("../output/maxent/predictions/sep/avg_cloglog_199.79.asc")
sep628 <- raster("../output/maxent/predictions/sep/avg_cloglog_628.026.asc")
sep11@crs <- acrs
sep61@crs <- acrs
sep199@crs <- acrs
sep628@crs <- acrs
sep11 <- raster::mask(sep11, mcp)
sep61 <- raster::mask(sep61, mcp)
sep199 <- raster::mask(sep199, mcp)
sep628 <- raster::mask(sep628, mcp)

dec11 <- raster("../output/maxent/predictions/dec/avg_cloglog_11.7737.asc")
dec61 <- raster("../output/maxent/predictions/dec/avg_cloglog_61.1128.asc")
dec199 <- raster("../output/maxent/predictions/dec/avg_cloglog_199.79.asc")
dec628 <- raster("../output/maxent/predictions/dec/avg_cloglog_628.026.asc")
dec11@crs <- acrs
dec61@crs <- acrs
dec199@crs <- acrs
dec628@crs <- acrs
dec11 <- raster::mask(dec11, mcp)
dec61 <- raster::mask(dec61, mcp)
dec199 <- raster::mask(dec199, mcp)
dec628 <- raster::mask(dec628, mcp)

#2d plots
mar2d <- raster("../output/maxent/paper_plots/hotspot_mapping/mar_bin_0.5_2d_single.asc")
mar2d <- raster::mask(mar2d, mcp)
mar2d@crs <- acrs
jun2d <- raster("../output/maxent/paper_plots/hotspot_mapping/jun_bin_0.5_2d_single.asc")
jun2d <- raster::mask(jun2d, mcp)
jun2d@crs <- acrs
sep2d <- raster("../output/maxent/paper_plots/hotspot_mapping/sep_bin_0.5_2d_single.asc")
sep2d <- raster::mask(sep2d, mcp)
sep2d@crs <- acrs
dec2d <- raster("../output/maxent/paper_plots/hotspot_mapping/dec_bin_0.5_2d_single.asc")
dec2d <- raster::mask(dec2d, mcp)
dec2d@crs <- acrs

@@

p <- levelplot(pstack, ylab = NULL, xlab = NULL, colorkey=list(space="bottom", at = my.at), par.settings = myTheme, layout = c(4, 4), margin = FALSE, scales=list(draw=FALSE), col.regions=rev(inferno(10)), at= my.at, names.attr = cls) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))+ latticeExtra::layer(sp.polygons(mcp, col = "dark grey"))
png("../output/maxent/paper_plots/bydepth.png", height = 1024, width = 1024)
p
dev.off()

@@

>>>>

#aea <- raster("../output/env/aea.tif") #the correct CRS
s <- shapefile("../data/env/landp/land-wgs84v2.shp") #made in arcgis
crs(s) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
#acrs <- aea@crs
mcp <- shapefile("../output/bio/minimum_convex_poly/mcp-wgs84.shp")
#ss <- raster::intersect(s, mcp)  #trim land file to mcp

@@

mar11 <- raster("../output/maxent/predictions/com-split/mar/avg_cloglog_11.7737.asc")
mar61 <- raster("../output/maxent/predictions/com-split/mar/avg_cloglog_61.1128.asc")
mar199 <- raster("../output/maxent/predictions/com-split/mar/avg_cloglog_199.79.asc")
mar628 <- raster("../output/maxent/predictions/com-split/mar/avg_cloglog_628.026.asc")
mar11@crs <- acrs
mar61@crs <- acrs
mar199@crs <- acrs
mar628@crs <- acrs
mar11 <- raster::mask(mar11, mcp)
mar61 <- raster::mask(mar61, mcp)
mar199 <- raster::mask(mar199, mcp)
mar628 <- raster::mask(mar628, mcp)

jun11 <- raster("../output/maxent/predictions/com-split/jun/avg_cloglog_11.7737.asc")
jun61 <- raster("../output/maxent/predictions/com-split/jun/avg_cloglog_61.1128.asc")
jun199 <- raster("../output/maxent/predictions/com-split/jun/avg_cloglog_199.79.asc")
jun628 <- raster("../output/maxent/predictions/com-split/jun/avg_cloglog_628.026.asc")
jun11@crs <- acrs
jun61@crs <- acrs
jun199@crs <- acrs
jun628@crs <- acrs
jun11 <- raster::mask(jun11, mcp)
jun61 <- raster::mask(jun61, mcp)
jun199 <- raster::mask(jun199, mcp)
jun628 <- raster::mask(jun628, mcp)

sep11 <- raster("../output/maxent/predictions/com-split/sep/avg_cloglog_11.7737.asc")
sep61 <- raster("../output/maxent/predictions/com-split/sep/avg_cloglog_61.1128.asc")
sep199 <- raster("../output/maxent/predictions/com-split/sep/avg_cloglog_199.79.asc")
sep628 <- raster("../output/maxent/predictions/com-split//sep/avg_cloglog_628.026.asc")
sep11@crs <- acrs
sep61@crs <- acrs
sep199@crs <- acrs
sep628@crs <- acrs
sep11 <- raster::mask(sep11, mcp)
sep61 <- raster::mask(sep61, mcp)
sep199 <- raster::mask(sep199, mcp)
sep628 <- raster::mask(sep628, mcp)

dec11 <- raster("../output/maxent/predictions/com-split/dec/avg_cloglog_11.7737.asc")
dec61 <- raster("../output/maxent/predictions/com-split/dec/avg_cloglog_61.1128.asc")
dec199 <- raster("../output/maxent/predictions/com-split/dec/avg_cloglog_199.79.asc")
dec628 <- raster("../output/maxent/predictions/com-split/dec/avg_cloglog_628.026.asc")
dec11@crs <- acrs
dec61@crs <- acrs
dec199@crs <- acrs
dec628@crs <- acrs
dec11 <- raster::mask(dec11, mcp)
dec61 <- raster::mask(dec61, mcp)
dec199 <- raster::mask(dec199, mcp)
dec628 <- raster::mask(dec628, mcp)

# #2d plots
# mar2d <- raster("../output/maxent/paper_plots/hotspot_mapping/mar_bin_0.5_2d_single.asc")
# mar2d <- raster::mask(mar2d, mcp)
# mar2d@crs <- acrs
# jun2d <- raster("../output/maxent/paper_plots/hotspot_mapping/jun_bin_0.5_2d_single.asc")
# jun2d <- raster::mask(jun2d, mcp)
# jun2d@crs <- acrs
# sep2d <- raster("../output/maxent/paper_plots/hotspot_mapping/sep_bin_0.5_2d_single.asc")
# sep2d <- raster::mask(sep2d, mcp)
# sep2d@crs <- acrs
# dec2d <- raster("../output/maxent/paper_plots/hotspot_mapping/dec_bin_0.5_2d_single.asc")
# dec2d <- raster::mask(dec2d, mcp)
# dec2d@crs <- acrs

@@

p <- levelplot(pstack, ylab = NULL, xlab = NULL, colorkey=list(space="bottom", at = my.at), par.settings = myTheme, layout = c(4, 4), margin = FALSE, scales=list(draw=FALSE), col.regions=rev(inferno(10)), at= my.at, names.attr = cls) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent")) #+ latticeExtra::layer(sp.polygons(mcp, col = "dark grey"))
png("../output/maxent/paper_plots/bydepth.png", height = 1024, width = 1024)
p
dev.off()

@@

#probabilty maps (selected)

xxxx
```{r}
library(raster)
library(rgdal)
library(rasterVis)
library(colorspace)

maplst <- list.files("../output/maxent/predictions/may", pattern = "^avg_clog.*.asc", full.names = TRUE)
maplst2 <- list.files("../output/maxent/predictions/sep", pattern = "^avg_clog.*.asc", full.names = TRUE)
brk <- seq(0, 1, 0.1) #for legend
lgc <- sequential_hcl(10, palette = "YlOrRd") #colour scheme from colorspace package
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

pras6 <- raster(maplst[37])
pras180 <- raster(maplst[14])
pras370 <- raster(maplst[28])
pras697 <- raster(maplst[41])
p2ras6 <- raster(maplst2[37])
p2ras180 <- raster(maplst2[14])
p2ras370 <- raster(maplst2[28])
p2ras697 <- raster(maplst2[41])
crs(pras6) <- apr
crs(pras180) <- apr
crs(pras370) <- apr
```

```{r}
crs(pras697) <- apr
crs(p2ras6) <- apr
crs(p2ras180) <- apr
crs(p2ras370) <- apr
crs(p2ras697) <- apr
ascname6 <- names(pras6)
ascname180 <- names(pras180)
ascname370 <- names(pras370)
ascname697 <- names(pras697)
a2scname6 <- names(p2ras6)
a2scname180 <- names(p2ras180)
a2scname370 <- names(p2ras370)
a2scname697 <- names(p2ras697)

```{r}
streams <- raster::shapefile("../data/env/landp/land-wgs84v2.shp")
ras <-

ggplot() + layer_spatial(data = streams, fill = "dark grey", colour = "transparent") + layer_spatial() + theme_void()

#2d maps for comb-maxent

```{r habitat classification on probability - >0.5xx}

for (m in 1:length(mthord)){
  mthna <- mthord[m]
  clogasc_list <- list.files(paste0("../output/maxent/predictions/com-split/", mthna), pattern = "^avg_cloglog_.*asc", full.names = TRUE)
  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    ascname <- gsub("avg_cloglog_", "", ascname)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/hotspot_mapping/", mthna,  "_binary_0.5_", ascname, ".asc"), overwrite = TRUE)
     plot(probbin, png(paste0("../output/maxent/paper_plots/hotspot_mapping/", mthna, "_binary_0.5_", ascname, ".png")), overwrite = TRUE)
       dev.off() # stops automatic saving of the plot to a png
  }
}

then create an summary map....
```{r >0.5 prob monthly 2D representation}
mthord <- c("mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for (m in 1:length(mthord)){
  mthna <- mthord[m]
  binaryprob_list <- list.files(paste0("../output/maxent/paper_plots/hotspot_mapping/"), pattern = paste0(mthna, "*_binary_0.5_.*.asc$"), full.names = TRUE)
  binstack <- stack(binaryprob_list)
  stacksum <- sum(binstack, na.rm = TRUE)
  writeRaster(stacksum, paste0("../output/maxent/paper_plots/hotspot_mapping/", mthna, "_bin_0.5_2d.asc"), overwrite=TRUE)
  plot(stacksum, png(paste0("../output/maxent/paper_plots/hotspot_mapping/", mthna, "_bin_0.5_2d.png")))
  dev.off()
}

now create summary maps where values are binary - not counts of cells
```{r}
binprob <- function(x){
  ifelse(x > 0, 1,
  ifelse(x <= 0, 0, NA))
}

  clogasc_list <- list.files("../output/maxent/paper_plots/hotspot_mapping", pattern = "*_bin_0.5_2d.asc", full.names = TRUE)
  for (cum in 1:length(clogasc_list)){
    cumasc <- raster(clogasc_list[cum])
    ascname <- names(cumasc)
    probbin <- calc(cumasc, fun = binprob) #creates raster layer with cell values based on the binprob function
    writeRaster(probbin, paste0("../output/maxent/paper_plots/hotspot_mapping/", ascname, "_single.asc"), overwrite = TRUE)
    plot(probbin, png(paste0("../output/maxent/paper_plots/hotspot_mapping/", ascname, "_single.png")), overwrite = TRUE)
    dev.off() # stops automatic saving of the plot to a png
  }
```

then plot the maps

ss <- shapefile("../data/env/landp/land-wgs84v2.shp") #made in arcgis
crs(ss) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 "
acrs <- crs(ss)
mcp <- shapefile("../output/bio/minimum_convex_poly/mcp-wgs84.shp")
#ss <- raster::intersect(s, mcp)  #trim to mcp

maplst <- list(mar2d, apr2d, may2d, jun2d, jul2d, aug2d, sep2d, oct2d, nov2d, dec2d)

pstack <- stack(maplst)

# my.at <- seq(0, 1, by = 0.1)
# mapTheme <- infernoTheme(region = rev(inferno(10)))

p <- levelplot(pstack, col.regions=c('white', 'red'), ylab = NULL, xlab = NULL, scales=list(draw=FALSE), layout = c(5, 2), names.attr = c("Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), margin = FALSE) + latticeExtra::layer(sp.polygons(ss, fill = "dark grey", col = "transparent"))+ latticeExtra::layer(sp.polygons(mcp, col = "dark grey"))
plot(p)
```

```{r}
require(data.table)
require(purrr)
require(lubridate)
require(tidyverse)

filenames <- list.files("../output/maxent/paper_plots/prob_by_depth/", pattern = "dis_prob_cells.csv", recursive = TRUE,full.names = TRUE)

all <- map_dfr(filenames, function(x) fread(x) %>% 
                       mutate(Month=substr(basename(x),1,3))) %>% 
  mutate(Probability = gsub(">0.9", "0.9 - 1", Probability),
         Depth = factor(round(Depth,1)),
         Depth = factor(Depth,ordered = TRUE, levels = rev(levels(Depth))),
         Month=factor(months(parse_date_time(Month,"%m")),
                      ordered = TRUE,
                      levels=months(parse_date_time(1:12,"%m"))))

#create a list of depths so you can set breaks for the x-axis (which is showing as the y-axis...)
dlst <- unique(all$Depth)
dlst <- as.character(dlst)
dlst <- as.numeric(dlst)
dlst <- sort(dlst)

  ggplot(all) +
  geom_col(aes(Depth, p_cells, fill = Probability),width=1) +
  coord_flip()+
  facet_wrap(~Month,ncol=5)+
  labs(y = "% Ocean at Depth", x = "Depth (meters)")+
  scale_fill_viridis(option="magma", discrete = TRUE, direction = -1, guide=guide_legend(nrow=2, byrow = TRUE))+
  theme_classic()+
  theme(legend.position = "bottom", axis.text.y = element_text(size=7), strip.background = element_blank()) +
  scale_x_discrete(breaks = c(dlst[1], dlst[5], dlst[10], dlst[15], dlst[20], dlst[25], dlst[30], dlst[35], dlst[40], dlst[47]))

ggsave("../output/maxent/paper_plots/test.png", dpi = 600)
```

```{r}
library(sf)
library(purrr)
library(raster)
library(lubridate)
library(tidyverse)

proj <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"

s <- st_read("../data/env/landp/land-wgs84v2.shp") %>% 
  st_set_crs(proj)

mcp <- st_read("../output/bio/minimum_convex_poly/mcp-wgs84.shp")

filelist <- list.files("../data/plot2-probmaps/",pattern="avg_cloglog*",recursive = TRUE,include.dirs = TRUE)

x <- stack(file.path("../data/plot2-probmaps/",filelist)) %>% 
  mask(mcp)

names(x) <- filelist

df <- x %>% 
  rasterToPoints() %>% 
  as.data.frame() %>% 
  gather(key = "variable", value = "value",-x,-y) %>% 
  mutate(variable=gsub(".asc","",variable),
         month=factor(months(parse_date_time(gsub("\\..*$", "",variable),"%m")),
                      ordered = TRUE,
                      levels=months(parse_date_time(1:12,"%m"))),
         depth=as.numeric(gsub("^.*_", "",variable)))

#remi code stops here

df$month <- str_sub(df$variable, start = 16, end = 18)

CapStr <- function(y) {
  c <- strsplit(y, " ")[[1]]
  paste(toupper(substring(c, 1,1)), substring(c, 2),
      sep="", collapse=" ")
}
df$month <- sapply(df$month, CapStr)

#remi code starts here

depthlab <- paste(unique(df$depth),"m")[c(1,3,2,4)]
names(depthlab) <- unique(df$depth)[c(1,3,2,4)]

ggplot(df)+
  geom_sf(data=mcp,fill='grey')+
  geom_raster(aes(x,y,fill=value))+
  geom_sf(data=mcp,fill="transparent")+
  scale_fill_viridis(option="magma",
                       direction=-1,
                       guide=guide_colourbar(barwidth=20))+
  facet_grid(depth~month,
             labeller = labeller(depth=depthlab))+
  theme_classic()+
  scale_x_continuous(breaks = seq(-70,-50,10))+
  theme(legend.position = "bottom",
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=45,vjust=1,hjust=1), strip.background = element_blank())
```
